refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-10-30 paper/reply.tex
Use plural (we) in response

\opening{Dear Dr Renaud}  % eg. Hello
Thank you for forwarding the kind comments of the referees towards my recently submitted manuscript (\#RG5158). I note that they were universally positive, with only minor adjustments to be made. These adjustments towards each referees comments are listed below, and I trust that they meet the requirements for publication in the \emph{Journal of Applied Crystallography}.

@@

\textbf{referee 2}
\begin{itemize}
\item \textbf{Resolve the question marks in the Sivia and Skilling reference} These references are completed successfully in our rendering of the latex document. I am unsure why they are not rendered properly by the submission gateway.
\item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
\item \textbf{Third-to-last line – shouldn't this read as $p(\theta|D,I)$ instead of $p(\theta|I,D)$?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
\end{itemize}

@@

\textbf{referee 4}
\begin{itemize}
\item \textbf{Missing references in 1-Introduction (after Sivia 2006)?} These references are completed successfully in our rendering of the latex document. I am unsure why they are not rendered properly by the submission gateway.
\item \textbf{Pauw et al may be added to the references list} This reference has been added.
\item \textbf{please complete the reference Nelson, A and Dewhurst C 2014 46 1338-1346} This reference has been completed.
\end{itemize}

>>>>

\opening{Dear Dr Renaud}  % eg. Hello
Thank you for forwarding the kind comments of the referees towards our recently submitted manuscript (\#RG5158). We note that they were universally positive, with only minor adjustments to be made. These adjustments towards each referees comments are listed below, and we trust that they meet the requirements for publication in the \emph{Journal of Applied Crystallography}.

@@

\textbf{referee 2}
\begin{itemize}
\item \textbf{Resolve the question marks in the Sivia and Skilling reference} These references are completed successfully in our rendering of the latex document. We are unsure why they are not rendered properly by the submission gateway.
\item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
\item \textbf{Third-to-last line – shouldn't this read as $p(\theta|D,I)$ instead of $p(\theta|I,D)$?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
\end{itemize}

@@

\textbf{referee 4}
\begin{itemize}
\item \textbf{Missing references in 1-Introduction (after Sivia 2006)?} These references are completed successfully in our rendering of the \LaTeX{} document. We are unsure why they are not rendered properly by the submission gateway.
\item \textbf{Pauw et al may be added to the references list} This reference has been added.
\item \textbf{please complete the reference Nelson, A and Dewhurst C 2014 46 1338-1346} This reference has been completed.
\end{itemize}
